### 2017-10-23 paper/sections/6_results.tex
paper: final read-through
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Figure~\ref{fig:composable-mechanisms} shows the runtime of the Cudele
mechanisms for a single client creating files in the same directory, normalized
to the time it takes to write 100K file create updates to the client's
in-memory journal ({\it i.e.} the ``Append Client Journal" mechanism).
``Stream" is an approximation of the overhead and is calculated by subtracting
the runtime of the job with the journal turned off from the runtime with the
journal turned on.  100K is the maximum recommended size of a directory in
CephFS; preliminary experiments with larger directory sizes show memory
problems.

{\it Poorly Scaling Data Structures:} Despite doing the same amount of work,
mechanisms that rely on poorly scaling data structures have large slowdowns for
the larger number of creates. For example, ``RPCs" which relies on the internal
CephFS directory structures has a \(90\times\) slowdown for 100K files. It is a
well-known problem that directory data structures do not scale when creating
files in the same directory~\cite{ren:sc2014-indexfs} and any mechanism that
uses these data structures will experience similar slowdowns. Other mechanisms
that write events to a journal) experience a much less drastic slowdown because
the journal data structure does not need to be scanned for every operation.
Events are written to the end of the journal without even checking the validity
({\it e.g.}, if the file already exists for a create), which is another form of
relaxed consistency because the file system assumes the application has
resolved conflicting updates in a different way.

% RPCs vs. apply: calls to metadata server vs. RADOS
{\it Overhead of RPCs:} ``RPCs" is \(66\times\) slower than ``Volatile
Apply" because sending individual metadata updates over the network is costly.
While ``RPCs" sends a request for every file create, ``Volatile Apply"
writes all the updates to the in-memory journal and applies them to the
in-memory data structures in the metadata server. While communicating the
decoupled namespace directly to the metadata server is faster, communicating
through the object store (``Nonvolatile Apply") is \(10\times\) slower.

% TODO: why is apply so slow.  
% apply: no CephFS changes, pulls/pushes same RADOS obj.
% v_apply vs. apply/persist: communicating through RADOS
{\it Overhead of ``Nonvolatile Apply":} The cost of ``Nonvolatile
apply" is much larger than all the other mechanisms.  That mechanism was not
implemented as part of Cudele -- it was a debugging and recovery tool packaged
with CephFS. It works by iterating over the updates in the journal and pulling
all objects that {\it may} be affected by the update.  This means that two
objects are repeatedly pulled, updated, and pushed: the object that houses the
experiment directory and the object that contains the root directory ({\it
i.e.} \texttt{/}).  The cost of communicating through the object store is shown
by comparing the runtime of ``Volatile apply" + ``Global persist" to
``Nonvolatile Apply". These two operations end up with the same final metadata
state but using ``Nonvolatile Apply" is clearly inferior.

% persist vs. save: one disk vs. many
{\it Parallelism of the Object Store:} Comparing ``Local" and ``Global
persist" demonstrates the bandwidth advantages of storing the journal in a
distributed object store. The ``Global Persist"
performance is \(1.5\times\) faster because the object store is leveraging the
collective bandwidth of the disks in the cluster. This benefit comes from the
object store itself but should be acknowledged when making decisions for the
application; the size of the object store can help mitigate the overheads of
globally persisting metadata updates.

@@

First we show how we can build application-specific subtrees by composing
mechanisms and that this approach results in more a scalable global namespace.
We start with clients creating files in private directories because this
workload is heavily studied in HPC~\cite{weil:sc2004-dyn-metadata,
ren:sc2014-indexfs, patil:fast2011-giga, zheng:pdsw2014-batchfs,
sevilla:sc15-mantle}, mostly due to checkpoint-restart~\cite{bent_plfs_2009}.
But the workload also appears in cloud workloads~\cite{xiao:socc15-shardfs},
where systems like Hadoop use the file abstraction to exchange work units to
workers or to indicate when jobs
complete~\cite{shvachko:login2012-hdfs-scalability}. A more familiar example is
uncompressing an archive ({\it e.g.}, \texttt{tar xzf}), where the file system
services a flash crowd of creates across all directories as shown in
Figure~\ref{fig:overhead-creates}.  We use this as a microbenchmark because it
allows us to control the size of the log, since each create creates a single
journal event. The workload is clients creating 100K files in private
directories in the same global namespace.

@@

To show the contention at the metadata server, in Figure~\ref{fig:mergescale}
we scale the umber of clients for the RPC per operation strategy used by many
POSIX IO systems and the decoupled namespace strategy used by DeltaFS. For
RPCs, we scale the number of clients making requests to the metadata server and
for the decoupled bars, we scale the number of concurrent journal merge
requests. So for the 30 clients data point, we are measuring the operations per
second for 30 client journals that land on the metadata server at the same
time. The ``create \& merge" bar adds the time it takes for clients to generate
the journal of events in parallel.

@@

The performance of decoupled namespaces is better than RPCs because we place no
restrictions on the validity of metadata inserted into the journal and avoid
touching poorly scaling data structures. We can scale linearly if we weaken our
consistency by never checking for the existence of files before creating files
({\it i.e.} only append \texttt{open()} requests to the journal).  When the
updates are merged by the metadata server into the in-memory metadata store
they never scan growing data structures.  Had we implemented the ``Create"
mechanism to include \texttt{lookup()} commands before \texttt{open()}
requests, we would have seen the poor scaling that we see with the ``RPCs"
mechanism.

@@

Next we show how Cudele can be programmed to block interfering clients using
the same problematic workload from Figure~\ref{fig:overhead-b}. In this
workload, clients create files in private directories and a separate client
creates files in each directory. This introduces false sharing and the metadata
server revokes capabilities on directories touched by the interfering client. While
HPC tries to avoid these situations with
workflows~\cite{zheng:pdsw2014-batchfs, zheng:pdsw2015-deltafs}, it still
happens in distributed file systems when users unintentionally access
directories in a shared file system.  We also have another client write to a
decoupled namespace and merge its updates at 90 seconds.  We only scale to 15
clients because the performance variability of a nearly overloaded metadata
server, in our case 18 clients, is too high.

Figure~\ref{fig:block-allow} plots the overhead of the slowest client and the
error bars are the standard deviation of 3 runs.  ``Interfere (Fig 3c)" is the
result from Figure~\ref{fig:overhead-b}; ``Interfere" uses the allow/block API
to return \texttt{-EBUSY} to interfering clients; and ``Isolated" is the
baseline performance without an interfering. Each subtree has ``RPCs" and
``Stream" enabled.  Results results are normalized to the runtime of a single
client creating files in a directory. Note that IndexFS has a similar behavior
to ``interfere" with leases, except clients block.

@@

The final use case shows how the API gives users fine-grained control of the
consistency semantics for niche or {\it ad-hoc} workflows.  Scientists use the
file system to check the progress of jobs using \texttt{ls} even though this
operation is notoriously heavy-weight~\cite{carns:ipdps09-pvfs,
eshel:fast10-panache} . The number of files or size of the files is indicative
of the progress. This practice is not too different from systems that use the
file system to manage the progress of jobs; Hadoop writes to temporary files,
renames them when complete, and creates a ``DONE" file to indicate to the
runtime that the task did not fail and should not be re-scheduled on another
node. In this scenario, Cudele users will not see the progress of decoupled
namespaces since their updates are not globally visible.  To help scientists
judge the progress of their jobs, Cudele clients have a ``namespace sync" that
sends batches of updates back to the global namespace at regular intervals.

% Does this implementation need to be described in the implementation?
Figure~\ref{fig:slowdown-sync} shows the performance degradation of a single
client writing updates to a decoupled namespace and pausing to send updates to
the metadata server. We scale the namespace sync interval to show the trade-off
of frequently pausing or writing large logs of updates.  We use an idle core to
log the updates and to do the network transfer. The client only pauses to fork
off a background process, which is expensive as the address space needs to
copied. The alternative is to pause the client completely and write the update
to disk but since this implementation is limited by the speed of the disk, we
choose the memory-to-memory copy of the fork approach.

>>>>

Figure~\ref{fig:composable-mechanisms} shows the runtime of the Cudele
mechanisms for a single client creating files in the same directory, normalized
to the time it takes to write 100K file create updates to the client's
in-memory journal ({\it i.e.} the Append Client Journal mechanism).
Stream is an approximation of the overhead and is calculated by subtracting
the runtime of the job with the journal turned off from the runtime with the
journal turned on.  100K is the maximum recommended size of a directory in
CephFS; preliminary experiments with larger directory sizes show memory
problems.

{\it Poorly Scaling Data Structures:} Despite doing the same amount of work,
mechanisms that rely on poorly scaling data structures have large slowdowns for
the larger number of creates. For example, RPCs has a \(90\times\) slowdown
because it relies on the internal CephFS directory data structures. It is a
well-known problem that directory data structures do not scale when creating
files in the same directory~\cite{ren:sc2014-indexfs} and any mechanism that
uses these data structures will experience similar slowdowns. Other mechanisms
that write events to a journal) experience a much less drastic slowdown because
the journal data structure does not need to be scanned for every operation.
Events are written to the end of the journal without even checking the validity
({\it e.g.}, if the file already exists for a create), which is another form of
relaxed consistency because the file system assumes the application has
resolved conflicting updates in a different way.

% RPCs vs. apply: calls to metadata server vs. RADOS
{\it Overhead of RPCs:} RPCs is \(66\times\) slower than Volatile
Apply because sending individual metadata updates over the network is costly.
While RPCs sends a request for every file create, Volatile Apply
writes all the updates to the in-memory journal and applies them to the
in-memory data structures in the metadata server. While communicating the
decoupled namespace directly to the metadata server is faster, communicating
through the object store (Nonvolatile Apply) is \(10\times\) slower.

% TODO: why is apply so slow.  
% apply: no CephFS changes, pulls/pushes same RADOS obj.
% v_apply vs. apply/persist: communicating through RADOS
{\it Overhead of Nonvolatile Apply:} The cost of Nonvolatile
Apply is much larger than all the other mechanisms.  That mechanism was not
implemented as part of Cudele -- it was a debugging and recovery tool packaged
with CephFS. It works by iterating over the updates in the journal and pulling
all objects that {\it may} be affected by the update.  This means that two
objects are repeatedly pulled, updated, and pushed: the object that houses the
experiment directory and the object that contains the root directory ({\it
i.e.} \texttt{/}).  The cost of communicating through the object store is shown
by comparing the runtime of Volatile Apply + Global Persist to
Nonvolatile Apply. These two operations end up with the same final metadata
state but using Nonvolatile Apply is clearly inferior.

% persist vs. save: one disk vs. many
{\it Parallelism of the Object Store:} Comparing Local and Global
Persist demonstrates the bandwidth advantages of storing the journal in a
distributed object store. The Global Persist
performance is \(1.5\times\) faster because the object store is leveraging the
collective bandwidth of the disks in the cluster. This benefit comes from the
object store itself but should be acknowledged when making decisions for the
application; the bandwidth of the object store can help mitigate the overheads of
globally persisting metadata updates.

@@

First we show how we can build application-specific subtrees by composing
mechanisms and that this approach results in more a scalable global namespace.
We start with clients creating files in private directories because this
workload is heavily studied in HPC~\cite{weil:sc2004-dyn-metadata,
ren:sc2014-indexfs, patil:fast2011-giga, zheng:pdsw2014-batchfs,
sevilla:sc15-mantle}, mostly due to checkpoint-restart~\cite{bent_plfs_2009}.
But the workload also appears in cloud workloads~\cite{xiao:socc15-shardfs},
where systems like Hadoop use the file abstraction to exchange work units to
workers or to indicate when jobs
complete~\cite{shvachko:login2012-hdfs-scalability}. A more familiar example is
uncompressing an archive ({\it e.g.}, \texttt{tar xzf}), where the file system
services a flash crowd of creates across all directories as shown in
Figure~\ref{fig:overhead-creates}.  The workload is clients creating 100K files
in private directories in the same global namespace.

@@

To show the contention at the metadata server, in Figure~\ref{fig:mergescale}
we scale the number of clients for the RPC per operation strategy and the
decoupled namespace strategy. For RPCs, we increase the number of clients
making requests to the metadata server and for decoupled (the merge bars), we
increase the number of concurrent journal merge requests. So for the 30 clients
data point, we are measuring the operations per second for 30 client journals
that land on the metadata server at the same time. The ``create \& merge" bar
adds the time it takes for clients to generate the journal of events in
parallel. The experiment is run three times but the standard deviation is too
small to see.

@@

The performance of decoupled namespaces is better than RPCs because we place no
restrictions on the validity of metadata inserted into the journal and avoid
touching poorly scaling data structures. We can scale linearly if we weaken our
consistency by never checking for the existence of files before creating files
({\it i.e.} only append \texttt{open()} requests to the journal).  When the
updates are merged by the metadata server into the in-memory metadata store
they never scan growing data structures.  Had we implemented the Append Client
Journal mechanism to include \texttt{lookup()} commands before \texttt{open()}
requests, we would have seen the poor scaling that we see with the RPCs
mechanism.

@@

Next we show how Cudele can be programmed to block interfering clients using
the same problematic workload from Figure~\ref{fig:overhead-b}. In this
workload, clients create files in private directories and a separate client
interferes by creating more files in each directory. This introduces false
sharing and the metadata server revokes capabilities on directories touched by
the interfering client. While HPC tries to avoid these situations with
workflows~\cite{zheng:pdsw2014-batchfs, zheng:pdsw2015-deltafs}, it still
happens in distributed file systems when users unintentionally access
directories in a shared file system.  We only scale to 15 clients because the
performance variability of a nearly overloaded metadata server, in our case 18
clients, is too high.

Figure~\ref{fig:block-allow} plots the overhead of the slowest client and the
error bars are the standard deviation of 3 runs.  ``Interfere (Fig 3c)" is the
result from Figure~\ref{fig:overhead-b}; ``Interfere" uses the allow/block API
to return \texttt{-EBUSY} to interfering clients; and ``Isolated" is the
baseline performance without an interfering. Each subtree has RPCs and
Stream enabled.  Results are normalized to the runtime of a single
client creating files in a directory. Note that IndexFS has a similar behavior
to ``interfere" with leases, except clients block.

@@

The final use case shows how the API gives users fine-grained control of the
consistency semantics.  The use case is that users often leverage the file
system to check the progress of jobs using \texttt{ls} even though this
operation is notoriously heavy-weight~\cite{carns:ipdps09-pvfs,
eshel:fast10-panache} . The number of files or size of the files is indicative
of the progress. This practice is not too different from systems that use the
file system to manage the progress of jobs; Hadoop writes to temporary files,
renames them when complete, and creates a ``DONE" file to indicate to the
runtime that the task did not fail and should not be re-scheduled on another
node. In this scenario, Cudele users will not see the progress of decoupled
namespaces since their updates are not globally visible.  To help users
judge the progress of their jobs, Cudele clients have a ``namespace sync" that
sends batches of updates back to the global namespace at regular intervals.

% Does this implementation need to be described in the implementation?
Figure~\ref{fig:slowdown-sync} shows the performance degradation of a single
client writing updates to a decoupled namespace and pausing to send updates to
the metadata server. The error bars are the standard deviations of 3 runs. We
scale the namespace sync interval to show the trade-off of frequently pausing
or writing large logs of updates.  We use an idle core to log the updates and
to do the network transfer. The client only pauses to fork off a background
process, which is expensive as the address space needs to copied. The
alternative is to pause the client completely and write the update to disk but
since this implementation is limited by the speed of the disk, we choose the
memory-to-memory copy of the fork approach.
